---
title: "R Notebook"
output: html_notebook
---
Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.
When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed. 
```{r}
# Load the ncdf4 package
library(ncdf4)

# Open the netCDF file for reading
nc <- nc_open("data_copernicus-echantillon/test.nc")

# Read the data from the variable
print(nc)
```

```{r}

lon <- ncvar_get(nc, "lon")
nlon <- dim(lon)
print(nlon)
head(lon)

lat <- ncvar_get(nc, "lat")
nlat <- dim(lat)
print(nlat)
```

```{r}

time <- ncvar_get(nc, "time")
print(time)
```

```{r}
tunits <- ncatt_get(nc, "time", "units")
nt <- dim(time)
nt
```

```{r}
tunits
```
```{r}
tmp_array <- ncvar_get(nc, "Temperature_Air_2m_Mean_24h")
#tmp_array[tmp_array==fillvalue$value] <- NA
print(tmp_array)
```
```{r}
tmp_array[1,]
```

```{r}
lat = rev(lat)
```
```{r}
dim(tmp_array)
dim(lat)
dim(lon)
```
```{r}
for (i in 1:dim(lon)) {
  tmp_array[i,] = rev(tmp_array[i,])
}
```

Pour voir les variables dans le workspace : ls() dans la console
```{r}
library(lattice)
library(RColorBrewer)


image(lon, lat, tmp_array, col=rev(brewer.pal(10, "RdBu")))
```
```{r}
grid <- expand.grid(lon=lon, lat=lat)
cutpts <- c(246,266,268,270,272,274,276,278,280,282,284,304)
levelplot(tmp_array ~ lon * lat, data=grid, at=cutpts, cuts=12, pretty=T, 
          col.regions=(rev(brewer.pal(11,"RdBu"))))
```


```{r}
# Close the netCDF file
nc_close(nc)
```

Test GIT
